\documentclass{res} 
\usepackage{microtype}
\usepackage{url}
\usepackage{mathptmx}

\begin{document}
%\vspace*{-12pt}
%\moveleft.5\hoffset\centerline{\large\bf Devlin Mallory} % Your name at the top
%\vskip-3pt
%%\moveleft\hoffset\vbox{\hrule width 6.90in height .8pt} % Horizontal line after
\newdimen\linew
\linew=\textwidth
\advance\linew\hoffset 
%\fulline
%\moveleft\hoffset\centerline{ ddm231@gmail.com \qquad 6315 Roanoke Road, Oakland, CA, 94618\qquad (831) 234-5488 } % Your address
%\moveleft.5\hoffset\centerline{}

\name{Devlin Mallory\\\vspace{-10pt}}
\address{malloryd@math.utah.edu\qquad \url{https://devlin-mallory.github.io/} 
%\qquad 831.234.5488 
\\\vspace{-10pt} }
\setlength{\leftmargini}{-10pt}

\renewcommand\sectionfont{\large \sc}
\begin{resume}
%{\bf Interests:} Singularities, Frobenius summands, differential operators, positivity of vector bundles, jet~schemes, Macaulay2.

\section{Employment} 
\ \\
{\bf Basque Center for Applied Mathematics}, Postdoctoral Researcher\hfill Fall 2024
\\\\
{\bf University of Utah}, Wylie Assistant Professor Lecturer\hfill Fall 2021 -- Summer 2024
\\\\
{\bf University of Michigan}, NSF Graduate Fellow\hfill Fall 2015 -- Spring 2021
\section{Education} 
\ \\
{\bf University of Michigan}\hfill Fall 2015 -- Spring 2021
\\ PhD, Advisor: Mircea Musta\c{t}\u{a}
\\
\\
{\bf University of California, Berkeley} \hfill Fall 2009 -- Fall 2013\\B.A. Pure Mathematics (Honors),  B.A. Physics 
 %{\sl Summa cum laude} (GPA: 3.97) %\hfill Fall 2009 - Fall 2013 % \\ Pure Mathematics (Honors), Physics  \\



\section{Papers and preprints} 
%\bibliography{devlin}
\begin{itemize}
\item The tilting property for $F_*^e\mathcal O_X$ on Fano surfaces and threefolds.  arXiv:2405.14070.
\item Homogeneous coordinate rings as direct summands of regular rings.  Illinois Journal of Mathematics, 68(1), 2024.
\item Finite F-representation type for homogeneous coordinate rings of non-Fano varieties.  \'Epijournal de G\'eom\'etrie Alg\'ebrique, Volume 7, 2023.
\item An explicit self-duality (with Nikolas Kuhn, Vaidehee Thatte, and Kirsten Wickelgren). In \emph{Stacks Project Expository Collection}, LMS Lecture Note Series, number 480, Cambridge University Press, 2023.
\item Bigness of the tangent bundle of del Pezzo surfaces and D-simplicity. Algebra \& Number Theory 15(8), 2021.
\item
Minimal log discrepancies of determinantal varieties via jet schemes. Journal of Pure and Applied Algebra 225(2), 2021.
\item
Triviality of arc closures and the local isomorphism problem, Journal of Algebra 544(47), 2020.
\end{itemize}

\section{Invited research activities}
\begin{itemize}
\item Institute for Advanced Study Summer Collaborators Program, July 2024 (with Jack Jeffries, Claudia Miller, Josh Pollitz, and Eamon Quinlan-Gallego).
\item American Institute of Math Workshop on Macaulay2, Special Session on Recent Developments in Commutative Algebra, September 2023.
\end{itemize}
\section{Invited talks}
\begin{itemize}
\item Commutative Algebra and Algebraic Geometry in Tucson, May 2024.
\item Stony Brook University, Algebraic Geometry seminar, April 2024.
\item Math For All Inclusivity and Outreach Conference, April 2024.
\item MSRI/SLMath, Special Seminar on Finite $F$-Representation Type for Rings and Varieties, March 2024.
\item Joint Mathematics Meeting, Special Session on Recent Developments in Commutative Algebra, January 2024.
\item 
%``Finite F-representation type for homogeneous coordinate rings''
AMS Fall Central Sectional, Special Session on Commutative algebra, differential operators, and singularities, October 2023.
\item 
%``Direct Summands of Regular Rings''
University of Minnesota Commutative Algebra and Algebraic Geometry seminar, April 2022.
\item 
%``Differential operators on singular rings and the global geometry of projective varieties,''
University of Connecticut Algebra seminar, March 2021.
\item 
%``Bigness of the tangent bundle and differential properties of singularities,''
University of Utah Algebraic Geometry Seminar, October 2020.
\item 
%``D-simplicity in characteristic 0 and characteristic p,''
AMS Fall Eastern Sectional, Special Session on Algebraic Singularities in Arbitrary Characteristic, October 2020
\item 
%``D-simplicity in characteristic 0 and characteristic p,''
Differential Operators in Commutative Algebra Seminar, May 29 and June 5, 2020.
\item 
%``Triviality of jet closures and the local isomorphism problem,''
University of Michigan Commutative Algebra Seminar, October 2019.
\item 
%``Minimal log discrepancies of determinantal varieties via jet schemes,''
AMS Fall Central Sectional, AMS Contributed Paper Session on Algebra, Geometry and Lie Theory, September 2019.
%\item (poster presentation) 
%``Arc closures and the local isomorphism problem,''
%Midwest Algebraic Geometry Graduate Conference, March 2019.
\end{itemize}


\section{Teaching}
\begin{itemize}
\item Winter 2024: Math 4400 (introduction to number theory).
\item Fall 2023: Math 5510 (introduction to general topology).
\item August 2023: Co-organizer, new instructor training.
\item Winter 2023: Math 3160 (complex analysis)
\item Fall 2022: Math 1220 (calculus II)
\item Fall 2021: Math 1080 (precalculus)
\item Summer 2021: Co-instructor, Michigan Math and Science Scholars, course on cryptography.
\item Winter 2021: Math 115 (calculus I).
\item Fall 2020: Course co-coordinator, Math 105 (precalculus).
\item August 2020: Co-organizer, New instructor training.
\item Fall 2018:  Math 115 (calculus I).
\item  Winter 2018: Grader, Math 632 (algebraic geometry II).
\item  Fall 2017: Grader, Math 631 (algebraic geometry I).
\item  Winter 2016:  Math 105 (precalculus).
\item  Fall 2015:  Math 105 (precalculus).
\end{itemize}

\section{Organizational activities}
\begin{itemize}
\item Organizer, Macaulay2, Computational Algebraic Geometry and String Theory workshop and conference, held at the University of Utah, Spring 2024.
\item Organizer, Utah Algebraic Geometry Seminar, Fall 2022 -- Spring 2024
\item Organizer, Introduction to Algebraic Geometry Reading Group, Winter 2023.
\item Mentor, University of Michigan Directed Reading Program, Summer 2020.
\item Organizer, Student Algebraic Geometry Seminar, Fall 2018 -- Winter 2021.
\item Organizer, Seminar on singularities in algebraic geometry and  algebra, Fall 2018 -- Winter 2019.
\item Organizer, Summer graduate student minicourse series, 2018--2021
\end{itemize}

\section{Other professional activities}
\begin{itemize}
\item Contributor to the Macaulay2 ``Varieties'' package, September 2023 -- Present.
\item Developer of the Macaulay2 ``DirectSummands'' package, July 2023 -- Present.
\item Reviewer, AMS Mathematical Reviews, 2023 -- Present.
\item Reviewer, zbMath Open, 2022 -- Present.
\end{itemize}

\section{Awards}
\begin{itemize}
\item University of Utah Outstanding Postdoc Award, April 2023.
\item University of Michigan Math Department Graduate Student Award, for “contributions to the scholarly life of the Mathematics department,” May 2019.
\item NSF Graduate Research Fellowship, 2015–2020.
\item Dorothea Klumpke Roberts Prize in Mathematics, Department of Mathematics, UC Berkeley, May 2014.
\item Honors in Mathematics, Department of Mathematics, UC Berkeley, December 2013.
\item Highest Honors, Budapest Semesters in Mathematics, May 2013.
\item Most Outstanding Presentation, Young Mathematicians Conference, Ohio State University, July 2012.
\item Phi Beta Kappa, UC Berkeley Chapter, June 2012.
\end{itemize}
\end{resume}
\end{document}
